{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
More fpcr estimation theory

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coeffieicnt function at the same parameter $L$ that was used for the approximation of the principal components and scores.

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon(\omega) \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon(\omega)
			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	\subsection{Draft-Overview}
	\begin{itemize}
		\item Motivate Karhunen-Loeve-Expansion and Eigenbasis from PCA		
		\item Explain Scalar-on-Function Regression
		\item Estimation through basis-expansion (incl. Eigenbasis) [and estimation with roughness penalty]
		\item Address approximation error due to basis-truncation
	\end{itemize}

>>>>

	If we additionally derive and approximate the principal components and corresponding scores using a truncated basis representation as in Equation \ref{score_approx} we obtain the following. To not complicate things more than necessary, the following equation assumes that the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ was used in the derivation of the principal components and the expansion of the coefficient function. Additionally, the following approximation also truncates the basis for the expansion of the coefficient function at the same parameter $L$ that was used for the approximation of the principal components and scores. The parameter $M$ corresponds to the chosen number of principal components and therefore constitutes another choice in the approximation.

	\begin{equation}
		\begin{split}
			y_i & \approx {\color{teal}\alpha + \sum_{j = 1}^{L} b_j \int_{0}^{1} \phi_j(s) \hat{\mu}(s) \mathrm{d}s} +  \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1} {\color{blue}\hat{\nu}^{m,L}(s)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
			& \approx {\color{teal} \tilde{\alpha}} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} \sum_{j = 1}^{L} b_j \int_{0}^{1}{\color{blue}\left(\sum_{k = 1}^{L} n_{k}^m \phi_{k}(s)\right)} \phi_j(s) \mathrm{d}s \right] + \epsilon_i \\
			& \approx \tilde{\alpha} + \sum_{m  = 1}^{M} \left[ \tilde{\xi}^{m,L}_{i} {\color{red}\sum_{j = 1}^{L} \left[ b_j \sum_{k = 1}^{L} n_{k}^m \int_{0}^{1} \phi_{k}(s) \phi_j(s) \mathrm{d}s \right]} \right]+ \epsilon_i
			= \tilde{\alpha} + \sum_{m  = 1}^{M} \tilde{\xi}^{m,L}_{i} {\color{red}\tilde{\beta}^{m,L}}+ \epsilon_i
		\end{split}
	\end{equation}

@@
